---
title: "Kermit Perceptions Rank Based Test"
author: "Sam Smith"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
Bonjour mon amie! - Comment-vas-tu?
=======
Bonjour mon amie! - Comment-vas-tu? 

random testing - natalie
>>>>>>> 188aafcf706e2cf8299375ef9b2aada7ed1b486d


```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

frog_hist <- ggplot(kermit, aes(x= Score.pre)) +
  geom_histogram(bins=4) +
  facet_wrap(~Gender)
```
Perform rank-based comparisons using Mann-Whitnet U and Wilcoxon-Signed Rank

Question: Is there a significant difference in pre-talk ranks aof Kermit for Male and Female respondents?  

```{r}
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data =.) 

#Null Hypothesis: There is NOT a significant difference in ranks for  

#Alternative: There is a significant difference in ranks for male and female respondents

mwu_kermit
```

"There was no significant difference in ranks for male and female respondents (w= 155.5, p=0.4, alpha=0.05)"

Next question (collaborators):

Is there a significant change in Kermit rankings before and after his Bren talk?

```{r}
wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

#Null: There isn't a significant difference in ranks for pre and post talk scores

wsr_kermit


```
 There is no significant difference in ranks for pre and post scores 
